An Embedding Framework for Consistent Polyhedral Surrogates

### 2021-06-24 poly-embed-journal/poly-embed-journal.tex
Cleaning up Lemma X, organizing, and making notation d vs \Y consistent

\subsection{Phase 1: construct $\V^*$}
Suppose we have a finite set $\V \subset \reals_+^d$.

@@

\begin{itemize}
\item Define $G = \{(x,c) \mid c \leq g(x)\} \subseteq \reals^d \times \reals$ to be the hypograph of $g$.
\item We define $H^+_v := H^+_{([v;-1], 0)}$ for a $v \in \reals^d_+$, where $[v; -1]\in\reals^d_+\times\reals$.
\item Additionally, denote $H_y^+ := H_{([e_y; 0], 0)}^+$ for any $y \in [d]$. % \{ (x,c) \in \reals^\Y \times \reals \mid x_y \geq 0\}$.
\item Again, we let $H_v := H_{([v;-1], 0)}$ for $v \in \reals^d_+$.

\item Define $F_v := H_v \cap G$ for any $v\in\reals^d_+$.

@@

\begin{claim}
	$G = \cap \H$.
\end{claim}
\begin{proof}
	$(x,c) \in G \iff g(x) - c \geq 0 \iff \min_{v \in \V}\inprod{v}{x} - c \geq 0$ and $x \in \reals_+^d$, which is true if and only if $\inprod{v}{x} - c \geq 0 \,\forall v \in \V$ and $x_y \geq 0$ for all $y$.
	In turn, this statement holds if and only if $(x,c) \in H^+_v$ for all $v \in \V$ and in $H^+_y$ for all $y \in \Y$, so $(x,c) \in \cap \H$.
\end{proof}

\begin{claim}
	$x \in \reals^d_+ \iff (x,c)\in \cap \H_\Y$ for all $c \in \reals$.
\end{claim}
\begin{proof}
	$\implies$ 
	Fix any $c \in \reals$.
	$x \in \reals^d_+ \iff x_y \geq 0$ for all $y \in \Y$.
	This means that for any $y \in \Y$, $(x,c) \in \{(x,c) \mid x_y \geq 0\} = H_y$.
	As $y$ and $c$ were arbitrary, this shows the forward direction.

@@

\begin{claim}
	Claim: $G$ is $(d+1)$-dimensional.  %\raf{$g$ is nonnegative on $\reals^\Y_+$, so $G$ contains $\{(x,c) \mid x\in\reals^\Y_+, c \leq 0\}$, which is full-dim.}
\end{claim}
\begin{proof}
	Since $g$ is nonnegative on $\reals_+^\Y$, $G$ therefore contains $\{(x,c) \mid x\in\reals^\Y_+, c \leq 0\}$, which is $(|\Y| + 1)$-dimensional.
\end{proof}

\begin{claim}
	\raf{This is the important general polyhedra result to cite/state.  Note: we'll have to work half-spaces of the form $H_{(w,\beta)}^+ = \{ z \in \reals^{n+1} \mid \inprod{z}{w} - \beta \geq 0\}$.}  
	%Since $G$ is a full-dimensional polyhedron, with a unique H-rep by [cite].
	There is some unique $\H^* \subseteq \H$ such that $G = \cap \H^*$. 
	%\jessie{$\H^* \subseteq \H$ since $G = \cap \H^* = \cap \H$; something about smallest cardinality here?}
	Moreover, for each $H_{(w_i, b_i)} \in\H^*$, the face $F_{(w_i, b_i)} = H_{(w_i, b_i)} \cap G$ is a facet. %\raf{make formal}
\end{claim}
  \begin{proof}
  	Since $G$ is full-dimensional, this follows immediately from Theorem~\ref{thm:polyhedron-uniquely-gen-facets}.
%	We know $G$ has a halfspace representation $G = G(H', \vec 0)$ uniquely determined by the facets of $G$ by \citep[Proposition 4.5]{gallier2008notes} \jessie{Another reference: Ziegler Proposition 2.15 analagous extension}.
%	Take $\H' := \H_{H'}$; we claim that $\H' \subseteq \H$ and $G = \cap \H'$. \jessie{$\H' \subseteq \H$ seems to follow from Proposition 8.5 from \url{https://people.inf.ethz.ch/fukudak/lect/pclect/notes2014/PolyComp2014.pdf}}
  \end{proof}

\begin{claim}
	$\H_\Y \subseteq \H^*$.
\end{claim}
\begin{proof}
	If there was a $y \in \Y$ such that $H_y = \{(x,c) \mid x_y \geq 0\}$ was not in $\H^*$, then we would either have some $c_1 > 0$ such that $\{(x,c) \mid x_y \geq c_1\} \in \H^*$, or we have a point $x$ such that $x_y < 0$ but $g(x) > -\infty$.
	The first cannot happen as we take $g$ to be defined (and finite) on $x = e_y \in \reals^d_+$.
	Moreover, the second cannot be true by construction of $g$ including the $0-\infty$ indicator on $\reals^d_+$.	
\end{proof}

\begin{claim}
  There is a unique finite set $\V^* \subseteq \reals^\Y_+$ such that $\H^* = \H_\Y \cup \H_{\V^*}$.
  Moreover, $F_v$ is a facet of $G$ for each $v\in\V^*$.
\end{claim}
\begin{proof}
\raf{Argue that all facets of $G$ are an $H_y \cap G$ or some $H_v \cap G$.  Thus, we can define $\V^*$ by $\H_\Y \cup \H_{\V^*} = \H^*$.  (I.e., $\H^* \setminus \H_\Y = \H_{\V^*}$ for some $\V^*$.)}

Since $G$ is full-dimensional, all facets of $G$ are uniquely determined by the hyperplanes $H$ whose halfspaces $H^+$ compose $\H^*$.
Any facet $F$ must then be some intersection of an $H_y \cap G$ or $H_v \cap G$.
Take $\V^*$ to be the set of such $H_v$ hyperplanes.
%Since $\H_\Y \subseteq \H^*$, we can consider $\H_{\V^*} := \H \setminus \H_{\Y}$, and $\V^*$ to be the set generating $\H_{\V^*}$.

The moreover follows immediately since $\H_{\V^*} \subseteq \H^*$ and every $H^+ \in \H^*$ defines a facet by Theorem~\ref{thm:polyhedron-uniquely-gen-facets}.
%	First, observe that by construction, $H_v = \{(x,c) \mid \inprod{v}{x} - c \geq 0\}$ is a valid inequality for $G$, and thus $F_v$ is a face of $G$ by definition.
%	To see that $F_v$ is a facet, we must show it is $\dim(G) - 1 = |\Y|$-dimensional.
%	This holds true if we can fit a $|\Y|$-dimensional ball in $F_v$.
%	If we could not fit such a ball in $F_v$, \jessie{contradict $\V$ minimum cardinality}
\end{proof}

\begin{corollary}
  Let $\V \subseteq \reals^\Y_+$ be a finite set such that $\H = \H_\Y \cup \H_\V$ satisfies $G = \cap \H$.  Then $\V^* \subseteq \V$.
\end{corollary}
\begin{proof}
  $\H_\Y \cup \H_{V^*} = \H^* \subseteq \H = \H_\Y \cup \H_{\V}$, ergo $\V^* \subseteq \V$.
\end{proof}

\begin{claim}
	$g(x) = \min_{v \in \V^*}\inprod{v}{x} - \delta(x \mid \reals_+^d)$
\end{claim}
\begin{proof}
	$G = \cap \H = \cap \H^* = \cap (\H_\Y \cup \H_{\V^*}) = \{(x,c) \in \reals_+^d \times \reals \mid \inprod{v^*}{x} \geq c$ for all $v^* \in \V^* \}$.
	Since $G$ is the hypograph of $g$, this means $g$ can be written as 
	$g(x) = \min_{v \in \V^*}\inprod{v}{x} - \delta(x \mid \reals^d_+)$. 
\end{proof}

@@

@@

\begin{claim}
	For all $x\in\reals^\Y_+$, there exists $v^*\in\V^*$ such that $H_{v^*}$ supports $G$ at $(x,g(x))$.
\end{claim}
\begin{proof}
%We can write any face $F = H \cap G = \{(x',c) \in \reals_+^{d} \mid \inprod{x'}{v} = c = g(x')\}$.
%Since $H_v^+$ must be a valid halfspace to define a face, we know that $G \subseteq H_v^+$.
%%If there was no $v \in \V^*$ such that $x \in F_v$, 
%Since $\H^* = \H_\Y \cup \H_{\V^*}$, if there was no $v \in \V^*$ such that $x \in F_v = F$, it must be the case that $\min_{H_v \in \H_\Y} \inprod{v}{x} = \min_{y \in \Y} x_y = g(x) = 0$ by construction of the halfspaces in $\H_\Y$. %, and we must have $x \not \in \reals_{++}^\Y$.
%
%\jessie{If $g$ is not locally constant}
%Since $g$ is continuous on $\reals^d_+$ (as it is convex), and not constant \jessie{??}, there must be some $x' \in B(x,\epsilon) \cap \reals_+^\Y$ such that $g(x') > 0$ and therefore no $y \in \Y$ would define a face $F_{v^*}$ supporting $G$ at $x'$.
%(We know such a face exists as $G$ is polyhedral and finite.)
%That $v^*$ must then be in $\V^*$, and we claim $\inprod{v^*}{x} = 0$, which would imply $H_{v^*}$ also supports $G$ at $x$.
%If $\inprod{v^*}{x} > 0 = g(x)$ (recall $g$ nonnegative on $\reals_+^\Y$) then we contradict continuity of $g$ on $\reals_+^\Y$. 
%Therefore, we must have $\inprod{v^*}{x} = 0$, and thus $H_{v^*}$ also supports $G$ at $x$.
%\jessie{Not the level of rigor that we want.  Also using lots of polyhedral structure here.}
%%First, $\inprod{v^*}{x} \geq 0$ by definition of $g$ nonnegative on $\reals_+^\Y$, and $\leq 0$

\jessie{Notes in meeting:
	For any $x \in \reals^d_+$, consider $v^* \in \argmin_{v \in \V} \inprod{v}{x}$.
Argue $G \subseteq H^+_{v^*}$ by definition.
Argue support: $g(x) = \inprod{v^*}{x}$.  WTS $(x,g(x)) \in G$.  Already have $(x,g(x)) \in H_{v^*}$.}

By Claim 7\jessie{make reference}, we know that $g(x) = \min_{v \in \V^*}\inprod{v}{x}$.
In particular, consider $v^* \in \argmin_{v \in \V^*}\inprod{v}{x}$; we claim that $H_{v^*}$ supports $G$ at $(x,g(x))$.
First, $G \subset H^+_{v^*}$ by definition of $G$ as the intersection of halfspaces.
Thus, it us just left to show that $(x, \inprod{v^*}{x}) \in H_{v^*} \cap G$.
$H_{v^*} = \{(x,c) \mid \inprod{v^*}{x} = c\}$.
By definition of $g$, we have $(x,g(x)) = \inprod{v^*}{x}$, so $(x,g(x)) \in H_{v^*}$.
Moreover, $(x,g(x)) \in G = \{(x,c) \mid g(x) \geq c\}$ trivially since $g(x) \geq g(x)$.

%\jessie{Claim: $x$ must be on boundary of $\reals_+^\Y$ and therefore $g(x) = 0$, and we have a matchy matchy with a $v^* \in \V^*$.}

%\jessie{If $x \in \reals_{++}^\Y$, then}

%As these halfspaces are vertical, we have $g(x) = -\infty$, which does not support $G$ at $(x, g(x))$ since $x \in \reals_+^\Y$, yielding a contradiction.
%\jessie{Don't like this. Slash not true.  There's something implicit about all the normals being in $\R^d_-$ and $x \in \reals^d_+$.  Haven't proven the first claim}
%We claim $\cup_{v \in \V}\pi(F_v) = \reals_+^\Y$.
%If there was a $v \in \V$ such that $\pi(F_v) \not \subseteq \reals_+^\Y$, this would imply there is some $x \not \in \reals_+^\Y$ such that $\inprod{x}{v} = c < \infty = g(x)$, contradicting $F_v$ supporting $g$ at $x$.
%Thus, $\cup_{v \in \V} \pi(F_v) \subseteq \reals_+^\Y$.
%Now for the other direction of subset inclusion, observe that for all $x \in \reals^\Y_+$, we have $g(x) = f(x) = \min_{v \in \V}\inprod{v}{x}$, so there is a $v \in \V$ supporting $g$ at $x$, and therefore $x \in \pi(F_v)$ for some $v \in \V$, and is therefore in the union of projections.
%As we have shown both directions of set inclusion, we must have $\cup_{v \in \V}\pi(F_v) = \reals_+^\Y$.	
\end{proof}

\begin{corollary}
	$\cup_{v\in\V^*} \pi(F_v) = \reals^\Y_+$.
	% \jessie{Not sure how to show this, but intuitively, this is saying that the projection of the facets union to $\reals^\Y_+$.}
\end{corollary}

\raf{From notes 6/21/2021 COMMENTED OUT}

\begin{itemize}
	\item REP $\iff$ $\V^* \subseteq L(R')$
	\item REP $\iff \Theta \subseteq \{\Gamma_r | r \in \R'\}$.
	\item $\Theta$ == Full-dim
	\item Lev sets subset $\theta$
\end{itemize}

\begin{claim}[6/21/2021]
  For $\V' \subseteq \V$, we have
  $\cup_{v\in\V'} \pi(F_v) = \reals^\Y_+ \iff \V^* \subseteq \V'$.\jessie{Will get us to REP $\iff$ $\V^* \subseteq L(R')$}
\end{claim}
\begin{proof}
  Would like to show
  $\cup_{v\in\V'} \pi(F_v) = \reals^\Y_+ \iff \cap(\H_\Y \cup \H_{\V'}) = G$ then apply Corollary 7\jessie{make reference}.

  Suppose $\cup_{v\in\V'} \pi(F_v) = \reals^\Y_+$.
  Take any $x\in\reals^\Y_+$.
  Then there exists $c \in \reals$ and $v\in\V'$ such that $(x,c) \in F_v$, and $c = \inprod{v}{x}$.
  \raf{Argue that we have $\cap(\H_\Y \cup \H_{\V'}) \subseteq G$}

  $\implies$ 
  Fix any $x \in \reals^\Y_+$.
  $(x,c) \in \H_\Y$ for all $c \in \reals$ by previous Claim \jessie{ref}, so we just need to show that $(x,c) \in \cap \H_{\V'} \implies (x,c) \in G$.

  We know there exists a $v' \in \V'$ and $c \in \reals$ such that $(x,c) \in F_{v'}$, and $c = \inprod{v'}{x} = g(x)$.
  Therefore $\inprod{v'}{x} = c = g(x) \leq \inprod{v}{x}$ for all $v \in \V$, so $(x,c) \in \cap \H_\V \implies (x,c) \in G = \cap (\H_\Y \cup \H_\V)$.

\raf{For Lemma X: NTS $\cup_{v\in\V} \pi(F_v) = \reals^\Y_+ \implies \V^* \subseteq \V$.}
\raf{If $G = \cap( \H_\Y \cup \H_\V)$...}

\begin{itemize}\setlength{\itemsep}{0pt}
\item Define $\V = L(\R) \subseteq \reals^\Y_+$ and $\H_{\V} = \{H_v^+ \mid v\in\V\}$.  Unlike above, these could be infinite sets.
\item Let $\H = \H_\Y \cup \H_{\V}$.
\end{itemize}
\begin{claim}
	$G = \cap\H$ by definition of $\risk{L}_+$.
\end{claim}
\begin{proof}
%  \raf{Let $(x,c) \in G$.  Show $(x,c)\in\cap \H$.  Then vice versa.  Or maybe iff once you get the hang of it.}
%  $(x,c) \in G = \{(x,c) \mid g(x) \geq c\}$.
%  Since $g(x) = \risk L_+(x)$, we then have $\min_{v \in \V}\inprod{x}{v} - \delta(x \mid \reals^\Y_+) = \inf_{r \in \R} \inprod{x}{L(r)}$\jessie{minnable doesn't really come in here, but want to be careful}.
%  Thus, for all loss vectors such that $v = L(r)$ we have $\inprod{v}{x} = \inprod{L(r)}{x} \geq c$, and therefore $(x,c) \in H^+_v$ for all $v \in L(\R)$, and is therefore in the intersection $H_v^+$.

%  $\implies$
%  Have $g(x) \geq c$... use $g=\risk{L}_+$... then for all loss vectors $v = L()$, $(x,c) \in H_v^+$.  Done.
%
%  Other dir: for any $(x,c) \in \cap \H$
\end{proof}

Need to use minimizable
Take $\V^*$ to be the unique finite set such that $\H^* = \H_\Y \cup \H_{\V^*}$, where $\H^*$ is the unique minimum halfspace representation for $G$ as in phase 1.

\begin{claim}
	$\H_{\V^*} \subseteq \H$
\end{claim}
\begin{proof}
	$\H_{\V^*} \subseteq \H^* \subseteq \H$.
	The first subset inclusion follows by construction of $\H_{\V^*}$, and the second follows from Theorem~\ref{thm:polyhedron-uniquely-gen-facets} as $\H^*$ is the unique minimum halfspace representation of $G$, and is finite.
	%%$G = \cap \H^*$ and $\H_{\V^*} \subseteq \H$.
	%since $\H_\Y \cup \H_{\V^*}$ is the unique min H-rep of $G$. \raf{not sure how to do this, since $\H$ could be infinite}
\end{proof}

\begin{claim} 
For all $v\in\reals^\Y_+$, if $H_v$ supports $G$, then $\dim(\pi(F_v)) = \dim(F_v)$.
\end{claim}
\begin{proof}

@@

@@

\begin{claim}If a $H_v \in \H$ does support $G$, then $F_{v} = H_{v} \cap G$ is a face of $G$, and thus a subset of a facet.
\end{claim}
\begin{proof}
	Since $H_v$ supports $G$, we know that $G \subseteq H_v^+$ (WLOG) and $F_v$ is not empty.
	Since $H^+_v$ is valid, we have $F_v = F_{([v;-1],0)}$ is a face by definition.

@@

\begin{claim}
	For any $v \in \V$, the face $F_{v}$ must be a subset of one of the $\V^*$ facets $F_{v^*}$ (as opposed to the vertical ones)
\end{claim}
\begin{proof}
$\{F_{v^*}\}_{v^* \in \V^*}$ is exactly the set of facets on $\reals_+^\Y$. \jessie{Cite}
Any $k$-face is contained in a facet (claim above).
Must therefore be one of these.

>>>>

\subsection{Phase 1: construct $\V^*$}
We will later consider losses over a finite set of outcomes $\Y$; for now, we use $\reals^\Y_+$ to denote $\reals^{|\Y|}_+$, and let $d := |\Y|+1$.
Suppose we have a finite set $\V \subset \reals_+^\Y$.

@@

\begin{itemize}
\item Define $G = \{(x,c) \mid c \leq g(x)\} \subseteq \reals^\Y_+ \times \reals$ to be the hypograph of $g$.
\item We define $H^+_v := H^+_{([v;-1], 0)}$ for a given $v$, where $[v; -1]\in\reals^\Y_+\times\reals$.
\item Additionally, denote $H_y^+ := H_{([e_y; 0], 0)}^+$ for any $y \in \Y$. % \{ (x,c) \in \reals^\Y \times \reals \mid x_y \geq 0\}$.
\item Similarly, we let $H_v := H_{([v;-1], 0)}$ for $v \in \reals^\Y_+$ and define $H_y$ analogously. 
\item Define $F_v := H_v \cap G$ for any $v\in\reals^\Y_+$.

@@

\begin{claim}\label{claim:G-intersection-H}
	$G = \cap \H$.
\end{claim}
\begin{proof}
	$(x,c) \in G \iff g(x) - c \geq 0 \iff \min_{v \in \V}\inprod{v}{x} - c \geq 0$ and $x \in \reals_+^\Y$, which is true if and only if $\inprod{v}{x} - c \geq 0 \,\forall v \in \V$ and $x_y \geq 0$ for all $y$.
	In turn, this statement holds if and only if $(x,c) \in H^+_v$ for all $v \in \V$ and in $H^+_y$ for all $y \in \Y$, so $(x,c) \in \cap \H$.
\end{proof}

\begin{claim}\label{claim:x-nonneg-orthant-iff-intersection-HY}
	$x \in \reals^\Y_+ \iff (x,c)\in \cap \H_\Y$ for all $c \in \reals$.
\end{claim}
\begin{proof}
	$\implies$ 
	Fix any $c \in \reals$.
	$x \in \reals^\Y_+ \iff x_y \geq 0$ for all $y \in \Y$.
	This means that for any $y \in \Y$, $(x,c) \in \{(x,c) \mid x_y \geq 0\} = H_y$.
	As $y$ and $c$ were arbitrary, this shows the forward direction.

@@

\begin{claim}\label{claim:G-full-dimensional}
	$G$ is $(|\Y| + 1)$-dimensional.  %\raf{$g$ is nonnegative on $\reals^\Y_+$, so $G$ contains $\{(x,c) \mid x\in\reals^\Y_+, c \leq 0\}$, which is full-dim.}
\end{claim}
\begin{proof}
	Since $g$ is nonnegative on $\reals_+^\Y$, $G$ therefore contains $\{(x,c) \mid x\in\reals^\Y_+, c \leq 0\}$, which is $(|\Y| + 1)$-dimensional.
\end{proof}

\begin{claim}\label{claim:G-unique-facets-Hstar}
	\raf{This is the important general polyhedra result to cite/state.  Note: we'll have to work half-spaces of the form $H_{(w,\beta)}^+ = \{ z \in \reals^{n+1} \mid \inprod{z}{w} - \beta \geq 0\}$.}  
	%Since $G$ is a full-dimensional polyhedron, with a unique H-rep by [cite].
	There is some unique $\H^* \subseteq \H$ such that $G = \cap \H^*$. 
	%\jessie{$\H^* \subseteq \H$ since $G = \cap \H^* = \cap \H$; something about smallest cardinality here?}
	Moreover, for each $H_{(w_i, b_i)} \in\H^*$, the face $F_{(w_i, b_i)} = H_{(w_i, b_i)} \cap G$ is a facet. %\raf{make formal}
\end{claim}
  \begin{proof}
  	Since $G$ is full-dimensional, this follows immediately from Theorem~\ref{thm:polyhedron-uniquely-gen-facets}.
%	We know $G$ has a halfspace representation $G = G(H', \vec 0)$ uniquely determined by the facets of $G$ by \citep[Proposition 4.5]{gallier2008notes} \jessie{Another reference: Ziegler Proposition 2.15 analagous extension}.
%	Take $\H' := \H_{H'}$; we claim that $\H' \subseteq \H$ and $G = \cap \H'$. \jessie{$\H' \subseteq \H$ seems to follow from Proposition 8.5 from \url{https://people.inf.ethz.ch/fukudak/lect/pclect/notes2014/PolyComp2014.pdf}}
  \end{proof}

\begin{claim}\label{claim:HY-subset-Hstar}
	$\H_\Y \subseteq \H^*$.
\end{claim}
\begin{proof}
	If there was a $y \in \Y$ such that $H_y = \{(x,c) \mid x_y \geq 0\}$ was not in $\H^*$, then we would either have some $c_1 > 0$ such that $\{(x,c) \mid x_y \geq c_1\} \in \H^*$, or we have a point $x$ such that $x_y < 0$ but $g(x) > -\infty$.
	The first cannot happen as we take $g$ to be defined (and finite) on $x = e_y \in \reals^\Y_+$.
	Moreover, the second cannot be true by construction of $g$ including the $0-\infty$ indicator on $\reals^\Y_+$.	
\end{proof}

\begin{claim}\label{claim:unique-set-loss-vectors-defining-facets}
  There is a unique finite set $\V^* \subseteq \reals^\Y_+$ such that $\H^* = \H_\Y \cup \H_{\V^*}$.
  Moreover, $F_v$ is a facet of $G$ for each $v\in\V^*$.
\end{claim}
\begin{proof}
\raf{Argue that all facets of $G$ are an $H_y \cap G$ or some $H_v \cap G$.  Thus, we can define $\V^*$ by $\H_\Y \cup \H_{\V^*} = \H^*$.  (I.e., $\H^* \setminus \H_\Y = \H_{\V^*}$ for some $\V^*$.)}

Since $G$ is full-dimensional, all facets of $G$ are uniquely determined by the hyperplanes $H$ whose halfspaces $H^+$ compose $\H^*$ by Claim~\ref{claim:unique-set-loss-vectors-defining-facets}.
Any facet $F$ must then be some intersection of an $H_y \cap G$ or $H_v \cap G$.

The moreover follows immediately since $\H_{\V^*} \subseteq \H^*$ and every $H^+ \in \H^*$ defines a facet by Theorem~\ref{thm:polyhedron-uniquely-gen-facets}.
\end{proof}

\begin{corollary}\label{cor:anything-gen-G-subset-Hstar}
  Let $\V \subseteq \reals^\Y_+$ be a finite set such that $\H = \H_\Y \cup \H_\V$ satisfies $G = \cap \H$.  Then $\V^* \subseteq \V$.
\end{corollary}
\begin{proof}
  $\H_\Y \cup \H_{\V^*} = \H^* \subseteq \H = \H_\Y \cup \H_{\V}$, ergo $\V^* \subseteq \V$.
\end{proof}

\begin{claim}\label{claim:g-gen-by-Vstar}
	$g(x) = \min_{v \in \V^*}\inprod{v}{x} - \delta(x \mid \reals_+^\Y)$
\end{claim}
\begin{proof}
	$G = \cap \H = \cap \H^* = \cap (\H_\Y \cup \H_{\V^*}) = \{(x,c) \in \reals_+^\Y \times \reals \mid \inprod{v^*}{x} \geq c$ for all $v^* \in \V^* \}$.
	Since $G$ is the hypograph of $g$, this means $g$ can be written as 
	$g(x) = \min_{v \in \V^*}\inprod{v}{x} - \delta(x \mid \reals^\Y_+)$. 
\end{proof}

@@

\begin{claim}\label{claim:vstar-supporting-G}
	For all $x\in\reals^\Y_+$, there exists $v^*\in\V^*$ such that $H_{v^*}$ supports $G$ at $(x,g(x))$.
\end{claim}
\begin{proof}
\jessie{Notes in meeting:
	For any $x \in \reals^d_+$, consider $v^* \in \argmin_{v \in \V} \inprod{v}{x}$.
Argue $G \subseteq H^+_{v^*}$ by definition.
Argue support: $g(x) = \inprod{v^*}{x}$.  WTS $(x,g(x)) \in G$.  Already have $(x,g(x)) \in H_{v^*}$.}

By Claim~\ref{claim:g-gen-by-Vstar}, we know that $g(x) = \min_{v \in \V^*}\inprod{v}{x}$.
In particular, consider $v^* \in \argmin_{v \in \V^*}\inprod{v}{x}$; we claim that $H_{v^*}$ supports $G$ at $(x,g(x))$.
First, $G \subset H^+_{v^*}$ by definition of $G$ as the intersection of halfspaces including $H^+_{v^*}$.
Thus, it us just left to show that $(x, \inprod{v^*}{x}) \in H_{v^*} \cap G$.
$H_{v^*} = \{(x,c) \mid \inprod{v^*}{x} = c\}$.
By definition of $g$, we have $(x,g(x)) = \inprod{v^*}{x}$, so $(x,g(x)) \in H_{v^*}$.
Moreover, $(x,g(x)) \in G = \{(x,c) \mid g(x) \geq c\}$ trivially since $g(x) \geq g(x)$.
\end{proof}

@@

\begin{corollary}\label{cor:projected-Vstar-faces-cover-pos-orthant}
	$\cup_{v\in\V^*} \pi(F_v) = \reals^\Y_+$.
\end{corollary}

\begin{claim}\label{claim:pi-preserves-dim}
	For all $v\in\reals^\Y_+$, if $H_v$ supports $G$, then $\dim(\pi(F_v)) = \dim(F_v)$.
\end{claim}
\begin{proof}

@@

\raf{From notes 6/21/2021}
\begin{itemize}
	\item REP $\iff$ $\V^* \subseteq \V' := L(\R')$\jessie{Claim~\ref{claim:Vprime-projected-faces-cover-iff-Vstar-subset-Vprime}}
	\item REP $\iff \jessie{\Lambda := \{\pi(F_v) \mid v \in \V^*\}; \Lambda \subseteq \{ \pi(F_{v}) \mid v \in L(\R')\}}$.
	\jessie{Claim~\ref{claim:Vprime-projected-faces-cover-iffprojected-faces-subsets}}
	\item $\Lambda$ == Full-dim \jessie{Claim~\ref{claim:projected-Vstar-faces-full-dim}.}
	\item Lev sets subset $\theta$ \jessie{Just work with $\pi(F_{v})$ where $v \in L(\R)$}
\end{itemize}

\begin{lemma}\label{lem:projected-faces-iff-support-iff-argmin}
	$x \in \pi(F_v) \iff (x,g(x)) \in F_v \iff v \in \argmin_{v' \in \V} \inprod{v'}{x}$
\end{lemma}
\begin{proof}
	\jessie{Don't like this in align environment}
	\begin{align*}
	x \in \pi(F_v) &\iff (x,g(x)) \in \{(x',c') \mid \inprod{v}{x'} = g(x) \} \\
	&\iff (x,g(x)) \in F_v \\
	&\iff (x,g(x)) \in \{(x',c') \mid \inprod{v}{x'} = \min_{v' \in \V} \inprod{v'}{x'}\} \\
	&\iff v \in \argmin_{v' \in \V}\inprod{v'}{x}
	\end{align*}
\end{proof}

\raf{For Lemma X: NTS $\cup_{v\in\V} \pi(F_v) = \reals^\Y_+ \implies \V^* \subseteq \V$.}
\raf{If $G = \cap( \H_\Y \cup \H_\V)$...}
\begin{claim}\label{claim:Vprime-projected-faces-cover-iff-Vstar-subset-Vprime}
  For $\V' \subseteq \V$, we have
  $\cup_{v\in\V'} \pi(F_v) = \reals^\Y_+ \iff \V^* \subseteq \V'$.\jessie{Will get us to REP $\iff$ $\V^* \subseteq L(R')$ (3)}
\end{claim}
\begin{proof}
  Would like to show
  $\cup_{v\in\V'} \pi(F_v) = \reals^\Y_+ \iff \cap(\H_\Y \cup \H_{\V'}) = G$ then apply Corollary~\ref{cor:anything-gen-G-subset-Hstar}\jessie{make reference}.

  Suppose $\cup_{v\in\V'} \pi(F_v) = \reals^\Y_+$.
  Take any $x\in\reals^\Y_+$.
  By Lemma~\ref{lem:projected-faces-iff-support-iff-argmin}, we have $(x,g(x)) \in F_v$.
  Let $c := g(x)$.
  \raf{Argue that we have $\cap(\H_\Y \cup \H_{\V'}) \subseteq G$}

  $\implies$ 
  Fix any $x \in \reals^\Y_+$.
  $(x,c) \in \cap \H_\Y$ for all $c \in \reals$ by Claim~\ref{claim:x-nonneg-orthant-iff-intersection-HY}, so we just need to show that $(x,c) \in \cap \H_{\V'} \implies (x,c) \in G$.
  We know there exists a $v' \in \V'$ such that $(x,g(x)) \in F_{v'}$, and $\inprod{v'}{x} = g(x)$.
  Therefore $\inprod{v'}{x} = g(x) \leq \inprod{v}{x}$ for all $v \in \V$, so $(x,g(x)) \in \cap \H_\V \implies (x,g(x)) \in G = \cap (\H_\Y \cup \H_\V)$.

\begin{claim}\label{claim:projected-Vstar-faces-full-dim}
	For all $v \in \V^*$, $\pi(F_v)$ is full dimensional in $\reals_+^\Y$.
	\jessie{$\Lambda$ is exactly the set of FDLS; Will lead to $\Theta$ are exactly the full dimensional level sets over simplex (6).}
\end{claim}
\begin{proof}
	By Claim~\ref{claim:unique-set-loss-vectors-defining-facets}, $F_v$ is a facet of $G$ in $\reals^d_+$, meaning it is $((|\Y| + 1) - 1)$-dimensional.
	Moreover, Claim~\ref{claim:pi-preserves-dim} states that the dimension of $F_v$ is preserved for each $v \in \V^*$.
	Thus, $\pi(F_v)$ is $|\Y|$-dimensional.
\end{proof}

\begin{itemize}\setlength{\itemsep}{0pt}
\item Define $\V = L(\R) \subseteq \reals^\Y_+$ and $\H_{\V} = \{H_v^+ \mid v\in\V\}$.  Unlike above, these could be infinite sets.
\item Let $\H = \H_\Y \cup \H_{\V}$.
\end{itemize}
\begin{claim}
	$G = \cap\H$ by definition of $\risk{L}_+$.
\end{claim}
\begin{proof}

\raf{Need to use minimizable}
Take $\V^*$ to be the unique finite set such that $\H^* = \H_\Y \cup \H_{\V^*}$, where $\H^*$ is the unique minimum halfspace representation for $G$ as in phase 1.

\begin{claim}
	$\H_{\V^*} \subseteq \H$
\end{claim}
\begin{proof}
	$\H_{\V^*} \subseteq \H^* \subseteq \H$.
	The first subset inclusion follows by construction of $\H_{\V^*}$, and the second follows from Theorem~\ref{thm:polyhedron-uniquely-gen-facets} as $\H^*$ is the unique minimum halfspace representation of $G$, and is finite.
	\jessie{Need to be more careful?}
	%%$G = \cap \H^*$ and $\H_{\V^*} \subseteq \H$.
	%since $\H_\Y \cup \H_{\V^*}$ is the unique min H-rep of $G$. \raf{not sure how to do this, since $\H$ could be infinite}
\end{proof}

Denote $\Lambda := \{\pi(F_v) \mid v \in \V^*\}$
\begin{claim}\label{claim:Vprime-projected-faces-cover-iffprojected-faces-subsets}
	For $\V' \subseteq \V$, we have $\cup_{v \in \V'} \pi(F_v) = \reals_+^\Y \iff \Lambda \subseteq \{ \pi(F_v) \mid v \in L(\R') \}$.
	\jessie{Will lead to rep iff $\Theta$ subset of level sets generated by $\R'$.}
\end{claim}
\begin{proof}
	$\implies$
	The result follows if $\V^* \subseteq \V'$, which is exactly the forward implication of Claim~\ref{claim:Vprime-projected-faces-cover-iff-Vstar-subset-Vprime}.
	Explicitly, for all $v \in \V^*$ we also have $v \in \V'$, so, $\pi(F_v) \in \Lambda \cap \{\pi(F_v) \mid v \in \V'\} = \Lambda$.

	$\impliedby$
	If $\Lambda \subseteq \{ \pi(F_v) \mid v \in L(\R') \}$, then $\cup \Lambda \subseteq \cup_{v \in \V'} \pi(F_v)$.
	By Corollary~\ref{cor:projected-Vstar-faces-cover-pos-orthant}, we have $\cup \Lambda = \reals_+^\Y$, so $\reals_+^\Y \subseteq \cup_{v \in \V'} \pi(F_v)$.
	The other direction of subset inequality following from $G$ being finite only on $\reals_+^\Y$.	
\end{proof}

@@

\begin{claim}If a $H_v \in \H$ does support $G$, then $F_{v} = H_{v} \cap G$ is a face of $G$, and thus a subset of a facet.
\end{claim}\label{claim:faces-contained-in-facets}
\begin{proof}
	Since $H_v$ supports $G$, we know that $G \subseteq H_v^+$ (WLOG) and $F_v$ is not empty.
	Since $H^+_v$ is valid, we have $F_v = F_{([v;-1],0)}$ is a face by definition.

@@

\begin{claim}\label{claim:vface-subset-some-vstar-face}
	For any $v \in \V$, the face $F_{v}$ must be a subset of one of the $\V^*$ facets $F_{v^*}$ (as opposed to the vertical ones)
\end{claim}
\begin{proof}
$\{F_{v^*}\}_{v^* \in \V^*}$ is exactly the set of facets of $G$ on $\reals_+^d$ by Theorem~\ref{thm:polyhedron-uniquely-gen-facets}.
Any $k$-face is contained in a facet by Claim~\ref{claim:faces-contained-in-facets}.
Must therefore be one of these.
